---
title: "finalProject"
author: "Ashley Brockway"
date: "12/9/2019"
output: html_document
---

##Setup
### options
Set up global options

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
knitr::opts_chunk$set(tidy=TRUE)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=70))
knitr::opts_chunk$set(fig.height=8, fig.width=12)
```  
## Introducing our Data and Methods {.tabset}

We found our dataset on [kaggle.](https://www.kaggle.com/azathoth42/myanimelist)  
The two collections we chose to use were anime_clean and userS_clean. The filtered versions of these documents is alse included to evaluate the data quality.  The cleaned version excludes inprobable entries.  The filtered version excludes users that have incomplete personal information.  

### Libraries
Load in needed libraries:  

```{r libraries, results='hide'}
# Run these if you don't have these libraries yet
# install.packages("tidyverse") 
# install.packages("data.table")
# install.packages("tm")  # for text mining
# install.packages("SnowballC") # for text stemming
# install.packages("wordcloud") # word-cloud generator 
# install.packages("RColorBrewer") # color palettes
# install.packages("plotly") #For pretty plots
# install.packages("vwr") #For regular expression functions
# install.packages("DT") # for interactive html tables
# install.packages("gridExtra") # for easy plot grids 
library(tidyverse) # For data processing and visualization
library(data.table) # For creating tables
library(tm)
library(SnowballC)
library(wordcloud)
library(RColorBrewer)
library(plotly)
library(vwr)
library(DT)
library(gridExtra)

spot_color = "#9ecae1" 
text_color = "#525252"
```
  
### File management
Create variables for directories
```{r file_management, echo=TRUE, results='hide'}
home.dir <- getwd()
data.dir <- './raw_data'
# viz.dir <- '.'
```

#### import
```{r echo=TRUE, results='hide'}
raw.data <- read.csv(file.path(home.dir, data.dir, "Hostel.csv"), na = c("NULL", "", "NA")) 
```

### Part 1: Descriptive Analysis  
```{r}
```

### Part 2: One Sample Statistical Inference  
#### Background for Test 
#### Hypotheses in Parameter Notation 
```{r} 
```
#### Hypothesis Test  
#### Results and Anylsis of Test 
### Part 3: Statistical Inference for Categorical Explanatory Variable
```{r}
```
#### Background for Test 
#### Hypotheses in Parameter Notation
#### Hypotheses Test for Population Proportion 
#### Results and Analysis 
### Part 4: Two Sample Statistical Inference  
```{r}
```
#### Background for Test 
#### Hypotheses in Parametric Notation 
#### Two Sample Test 
#### Results and Analysis 
### Part 5: Probability of A Stay being 'Worth it' Given Distance From City Center
#### Background 
```{r}
```
#### Question 
#### Method 
#### Execution 
#### By Cities 
#### Deriving Bayes' Law 
#### Results and Analysis 

### Conclusions 
#### Limitations  
#### Future Work and Questions  


  